---
title: "WorldPop Malawi - Household Estimate Triangulation Report"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: true
    toc_float: true
    toc_depth: 2
    self_contained: true
params:
  triangulation_csv: NULL
  triangulation_summary_csv: NULL
  distribution_summary_csv: NULL
  score_summary_csv: NULL
  distribution_plot_file: NULL
  alignment_score_pct_weight: NULL
  alignment_score_ci_bonus: NULL
---

```{css, echo=FALSE}
h2 {
  border-top: 3px solid #2980b9;
  padding-top: 14px;
  margin-top: 36px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

library(dplyr)
library(knitr)
library(kableExtra)

triangulation <- read.csv(
  params$triangulation_csv,
  stringsAsFactors = FALSE
)

triangulation_summary <- read.csv(
  params$triangulation_summary_csv,
  stringsAsFactors = FALSE
)

distribution_summary <- read.csv(
  params$distribution_summary_csv,
  stringsAsFactors = FALSE
)

score_summary <- read.csv(
  params$score_summary_csv,
  stringsAsFactors = FALSE
)
```

# Overview

This report compares household estimates from the ratio-change method with WorldPop growth-factor estimates for each Enumeration Area in Malawi.

```{r overview-placeholder}
summary_table <- data.frame(
  Measure = c(
    "Total number of EAs included",
    "Percentage of ratio-change estimates within WorldPop confidence interval",
    "Mean percentage difference",
    "Median percentage difference"
  ),
  `Ratio-change` = c(
    as.character(triangulation_summary$ratio_change_eas),
    rep("", 3)
  ),
  WorldPop = c(
    as.character(triangulation_summary$worldpop_eas),
    rep("", 3)
  ),
  Value = c(
    as.character(triangulation_summary$total_eas),
    sprintf("%.2f%%", triangulation_summary$pct_within_ci),
    sprintf("%.2f%%", triangulation_summary$mean_pct_diff),
    sprintf("%.2f%%", triangulation_summary$median_pct_diff)
  )
)

knitr::kable(summary_table, row.names = FALSE, format = "html") %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  kableExtra::column_spec(2:4, width = "12em")
```

# Distribution of Differences

```{r distribution-placeholder}
knitr::kable(
  distribution_summary,
  col.names = c("Statistic", "Percentage difference"),
  row.names = FALSE,
  digits = 2,
  format = "html"
) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  kableExtra::column_spec(2, width = "12em")

knitr::include_graphics(params$distribution_plot_file)
```

# Alignment Score Distribution

This section shows the distribution of EA alignment scores, which measure how well the ratio-change and WorldPop growth-factor estimates agree.

**Scoring Methodology:**
The alignment score ranges from 0 to 100 based on:
- **Percentage difference penalty**: `r params$alignment_score_pct_weight` points deducted per 1% difference
- **Confidence interval bonus**: `r params$alignment_score_ci_bonus` points added if ratio-change falls within WorldPop's confidence interval

Formula: `Score = min(100, max(0, 100 - (|pct_diff| * weight) + (within_ci ? bonus : 0)))`

```{r score-distribution}
score_table <- score_summary
score_table$percentage <- sprintf("%.2f%%", score_table$percentage)

knitr::kable(
  score_table,
  col.names = c("Confidence Level", "Number of EAs", "Percentage"),
  row.names = FALSE,
  format = "html",
  align = c("l", "r", "r")
) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover"),
    full_width = FALSE
  ) %>%
  kableExtra::column_spec(2, width = "12em") %>%
  kableExtra::column_spec(3, width = "12em")
```

# Directional Analysis

```{r direction-placeholder}
# Placeholder for comparing the number of EAs where each method is higher.
```

# Geographic Breakdown

```{r geography-placeholder}
# Placeholder for region- and district-level comparisons.
```

# Triage Targets

```{r triage-placeholder}
# Placeholder for identifying EAs with the greatest disagreement.
```

# Data Notes

```{r data-notes-placeholder}
# Placeholder for missing values, duplicate checks, and other data-quality notes.
```
